An Airdrop That Preserves Recipient Privacy

### 2019-01-12 paper/paper.tex
stash note from chat with Dima and Henry

>>>>

\rsw{stashed note from chat with Henry and Dima}
Possible objection: why doesn't sender just generate a bunch of phony keys
    and send all money to self?
In other words, why is this scheme better, from the verifiers' point of view,
    than the naive approach, i.e., sender generating a fresh key pair and
    sending secret key to recipient?
(Note that while the naive approach does not have existential unforgeability,
    that property does not prevent self-dealing if sender knows secret key.
Another way to say this is that the security property we need for the
    airdrop-to-Github-users case is stronger than existential unforgeability.)

One answer: for each RSA key $\PK = (n, e)$ to be paid, sender publishes
    the challenge $c = g^nh^s$ and (separately, i.e., without revealing
    correspondence) sender also publishes
$(\PK, s')$, $s' = E(\PK, (c',s)))$, $c' = H(g^nh^s)$.
In other words, the sender publishes a list of purported airdrop recipients
    separately from the list of airdrop challenge tokens.

If sender was dishonest with respect to any key, i.e., if for some $(\PK,
    s')$, any of $s', c', c, s$ is invalid, key's owner can reveal $(\hat{c}',
    \hat{s}) = D(\PK, s')$.
Then verifiers check that $s' = E(\PK, (\hat{c}', \hat{s}))$, and that
    either no corresponding $c$ exists, or that $c$ is not a commitment
    to $n$ with opening $s$.

\emph{Question:} do we need to make $E()$ deterministic for this to work
    (say, $r = H(\PK)$ in OAEP)?
